\bf Title here

### 2020-08-13 paper/paper.Rmd
modify according to issue #6

```{r origin-data, fig.cap="\\label{origin-data} The distribution of simulated data except x3"}
origin_dt_bi <- data_mult %>% 
  dplyr::select(-x3) %>% 
  gather(names, values) %>%
  mutate(names = as_factor(names))

@@

We form our first dataset using variables `x1`, `x2`, `x8`, `x9` and `x10` and run the guided tour with optimiser `search_better`. When the optimisation ends, the global object will be stored and printed (it can be turned off by supplying argument `print = FALSE`). Additional messages during the optimisation can be displayed by argument `verbose = TRUE`. Below shows the first ten rows of the global object. Notice that the tibble object allows the list-column `basis` to be printed out nicely with the dimension of the projection basis readily available.

@@

>>>>

```{r origin-data, fig.cap="\\label{origin-data} The distribution of simulated data except x3"}
origin_dt_bi <- data_mult %>% 
  dplyr::select(-c(x3, x8, x9, x10)) %>% 
  gather(names, values) %>%
  mutate(names = as_factor(names))

@@

We form our first dataset using variables `x1`, `x2`, `x8`, `x9` and `x10`,  run the guided tour with optimiser `search_better` and below shows the first ten rows of the global object.

@@

When the optimisation ends, the global object will be stored and printed (it can be turned off by supplying argument `print = FALSE`). Additional messages during the optimisation can be displayed by argument `verbose = TRUE`.  Notice that the tibble object allows the list-column `basis` to be printed out nicely with the dimension of the projection basis readily available.

### 2020-08-13 paper/paper.tex
modify according to issue #6

We form our first dataset using variables \texttt{x1}, \texttt{x2},
\texttt{x8}, \texttt{x9} and \texttt{x10} and run the guided tour with
optimiser \texttt{search\_better}. When the optimisation ends, the
global object will be stored and printed (it can be turned off by
supplying argument \texttt{print\ =\ FALSE}). Additional messages during
the optimisation can be displayed by argument \texttt{verbose\ =\ TRUE}.
Below shows the first ten rows of the global object. Notice that the
tibble object allows the list-column \texttt{basis} to be printed out
nicely with the dimension of the projection basis readily available.

@@

>>>>

We form our first dataset using variables \texttt{x1}, \texttt{x2},
\texttt{x8}, \texttt{x9} and \texttt{x10}, run the guided tour with
optimiser \texttt{search\_better} and below shows the first ten rows of
the global object.

@@

When the optimisation ends, the global object will be stored and printed
(it can be turned off by supplying argument \texttt{print\ =\ FALSE}).
Additional messages during the optimisation can be displayed by argument
\texttt{verbose\ =\ TRUE}. Notice that the tibble object allows the
list-column \texttt{basis} to be printed out nicely with the dimension
of the projection basis readily available.
